\documentclass[12pt]{letter}
\usepackage[top=0.3cm,bottom=0.3cm]{geometry}
\renewcommand{\baselinestretch}{1.1} %increases vert spacing of text
\synctex=1
\name{David Karapetyan}
\signature{\vspace{-0.5cm}David Karapetyan}
%\longindentation=0pt
\date{\vspace{0.5cm}\flushleft}
\begin{document}

\begin{letter}{}
\begin{center}
{\bf {\Large David Karapetyan}}
\end{center}

\begin{center}
{819 Hylan Hall, University of Rochester, NY 14607  \\ 
202-460-5173 \\  david.karapetyan@gmail.com
}
\end{center}
\hrule

\opening{Dear Dr. Bhandari:\\}
%
%
I would like to apply for a position as a data scientist in the new group
you are forming at IBM to improve and scale the Watson platform to enterprise business processes. I am currently the lead data scientist at
Rudin Management, where I designed and implemented a machine learning
engine which both forecasts and optimizes energy usage for the Rudin family's
portfolio of commercial high-rises. It is an ensemble engine which uses a number
of open-source tools, including pandas, scikit-learn,
statsmodels, MongoDB, and PostgreSQL.
In addition to the industry experience above,
my academic credentials include research experience as a Visiting Assistant Professor at the University of Rochester,
and a Ph.D. in mathematics from the University of Notre Dame.

I am very excited about the opportunity of applying state of the art statistical
research and tools to improve IBM's Watson technology, which I have read much
about in the media.  I have no doubt you are considering many candidates for the
team, but feel my background, industry experience, and passion for data
science make me a great fit.

If you have any questions, please do not hesitate to ask. It would be a pleasure to interview with you, and I hope to hear from you soon. Thank you for your time and consideration.


\closing{Sincerely,}


\end{letter}

\end{document}
