\documentclass[12pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage[latin1]{inputenc}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{framed}
\author{David Karapetyan}
\begin{document}

INTRODUCTION

PrescriptiveData was founded to provide real-time analytics and forecasting to
commercial and residential buildings, and is seeking an assistant data scientist
to join the analytics team and assist in the development of benchmarking and
predictive algorithms and models. Candidates will apply expertise to assist the
team lead in solving novel problems, ranging from adaptive contextual
experiments, to using machine learning to identify behavioral patterns for
building electricity usage, steam usage, occupancy, and other variables. 

RESPONSIBILITIES

Scientists will be expected to help design, maintain, and implement models using the
Python SciPy stack, as well as manage databases and an analytics cloud
infrastructure. 

Requirements
Bachelor in mathematics, computer science, or statistics from a top-20
university. 

PROGRAMMING

Candidates must have at least 2 years experience working with Python and the
SciPy stack, particularly with pandas and scikit-learn. Must have a good
knowledge of data structures and optimization best-practices

Knowledge of linux distributions, specifically Debian/Ubuntu. Knowledge of SQL
and MongoDB.

AT LEAST ONE OF THE FOLLOWING

Experience with field experiments, experimental design, missing data, survey sampling, and/or panel data.

AT LEAST ONE OF THE FOLLOWING

Experience with observational causal inference, cross-validation, Gaussian
processes, and regression adjustment

CLOSING

We are looking for the right kind of mind, one that can contribute immediately, but
that is also eager to learn and grow


\section{Developer \#1 (Assisting more with Algorithms Code)}
\subsection{Education}
\begin{enumerate}[a)]
	\item
		Ideally, someone from \textbf{MIT, Berkeley, Carnegie Mellon, Princeton}, or other
		top-ranked technical schools with an \textbf{undergraduate degree in
		computer science}. 
		Paying even \textbf{above market rate} for someone like that would pay off in the
		long term. 
	\item\label{itm:crit1} If there are a shortage of candidates, and we must be practical, then
		what becomes important is that the candidate have an \textbf{undergraduate
		degree in CS} from a top-25-school: \\
		\href{}{http://colleges.usnews.rankingsandreviews.com/best-colleges/rankings/national-universities}
	\item\label{itm:crit2} Theoretical knowledge of \textbf{data structures}, and lower level languages like
		\textbf{Assembly} or \textbf{C/C++}. Experience with \textbf{Python}

\end{enumerate}

The work in \textbf{analytics is different from a regular developer
job}: if a co-worker makes even a small mistake in code, or is a bit sloppy,
the forecasts can be way off, the code will run very slowly, or both. Being able to trust them is paramount; otherwise, they are just overhead.


\begin{framed}
	If requirements \ref{itm:crit1}) and \ref{itm:crit2}) are not met, please do not hire.
\end{framed}

\subsection{Experience}
\begin{enumerate}[a)]
	\item\label{itm:exp1}At least \textbf{2 years of Python} experience working with the SciPy stack,
		especially \textbf{Pandas and NumPy}.
	\item\label{itm:exp2}
		At least \textbf{1 year of experience with a linux distribution} (preferably
		Debian/Ubuntu, but can be others). 
	\item\label{itm:exp3} Familiarity with a database (can be of type NoSQL or SQL)
\end{enumerate}

\begin{framed}
	If requirements \ref{itm:exp1}) and \ref{itm:exp2}) are not met, please do not
	hire.
\end{framed}

\section{Developer \#2 (Assisting more with DB/Amazon Administration and Testing) }
\subsection{Education}
\begin{enumerate}[a)]
	\item
		Ideally, someone from \textbf{MIT, Berkeley, Carnegie Mellon, Princeton}, or other
		top-ranked technical schools with an \textbf{undergraduate degree in
		computer science}. 
		Paying even \textbf{above market rate} for someone like that would pay off in the
		long term. 
	\item\label{itm:critdevdb} If there are a shortage of candidates, and we must be practical, then
		what becomes important is that the candidate have an \textbf{undergraduate
		degree in CS} from a top-25-school: \\
		\href{}{http://colleges.usnews.rankingsandreviews.com/best-colleges/rankings/national-universities}

\end{enumerate}


\begin{framed}
	If requirement \ref{itm:critdevdb}) is not met, please do not hire.
\end{framed}

\subsection{Experience}
\begin{enumerate}[a)]
	\item\label{itm:exp1tester} At least \textbf{1 year DB admin} experience, preferably 
		with MongoDB, but SQL is fine too. 
	\item\label{itm:exp2tester}
		At least \textbf{1 year of Python} experience working with the SciPy stack,
		especially \textbf{Pandas and NumPy}. 
	\item\label{itm:exp3tester} Must have \textbf{2 years of unit and integration
		testing} experience, preferably in Python.
\end{enumerate}

\begin{framed}
	If requirements \ref{itm:exp1tester}) , \ref{itm:exp2tester}), and \ref{itm:exp3tester}) are not met, please do not hire.
\end{framed}

\end{document}
