\documentclass[12pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage[latin1]{inputenc}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{framed}
\author{David Karapetyan}
\begin{document}

Given the marketplace, and what I have accomplished so far at
Prescriptive Data:

\begin{enumerate}[a)]
	\item I am currently making $\$130,000$. 
	I am seeking more, and prefer to discuss the number in person.
\item A dental plan with full coverage for a variety of procedures for a small
	deductible (my current dental plan covers little other than a basic checkup. I
	know this from recent visits to the dentist).
\item A flexible work remote arrangement. 
\item More vacation time.
\item An office space. There is a free office available. The privacy and increased
	desk space alone would be beneficial. 
\item A more clear definition of my position at the company. I have 
	implicitly been the lead data scientist at Prescriptive Data for the past year.
	I would appreciate being given the title officially, and some more
	clarification of duties going forward, especially as we add employees and
	build out the team. Right now, it seems I am
	seen as some sort of mathematician/programmer, even though I have
	served a much more important role for Prescriptive Data this past year.
\item Clarification about equity, and potential bonuses in the future. Other
	startups and more established tech firms offer one, or both.
\item Clarification about projected growth of the company after June. For
	example, what are the projected future sales for the company? What will happen
	to the team if the projection is not met? How much capital do we currently
	have? What is the budget for new hires?
\item Clarification about corporate end-of-year raises for Prescriptive Data. 
\item Clarification about hours. For Rudin, it is 7 hours a day. It is not clear
	what the official hours are now for Prescriptive Data, and what they will
	be going forward. What happens if it turns out we are undermanned for the future?
\end{enumerate}

I hope to sit together and talk more at your earliest convenience. 
\end{document}
