%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beamer Presentation
% LaTeX Template
% Version 1.0 (10/11/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND THEMES
%----------------------------------------------------------------------------------------

\documentclass{beamer}

\mode<presentation> {

% The Beamer class comes with a number of default slide themes
% which change the colors and layouts of slides. Below this is a list
% of all the themes, uncomment each in turn to see what they look like.

%\usetheme{default}
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{Dresden}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

% As well as themes, the Beamer class has a number of color themes
% for any slide theme. Uncomment each of these in turn to see how it
% changes the colors of your current slide theme.

%\usecolortheme{albatross}
%\usecolortheme{beaver}
%\usecolortheme{beetle}
%\usecolortheme{crane}
%\usecolortheme{dolphin}
%\usecolortheme{dove}
%\usecolortheme{fly}
%\usecolortheme{lily}
%\usecolortheme{orchid}
%\usecolortheme{rose}
%\usecolortheme{seagull}
%\usecolortheme{seahorse}
%\usecolortheme{whale}
%\usecolortheme{wolverine}

%\setbeamertemplate{footline} % To remove the footer line in all slides uncomment this line
%\setbeamertemplate{footline}[page number] % To replace the footer line in all slides with a simple slide count uncomment this line

%\setbeamertemplate{navigation symbols}{} % To remove the navigation symbols from the bottom of all slides uncomment this line
}

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title[Major Progress]{Major Progress, Relative to TPO/Columbia} % The short title appears at the bottom of every slide, the full title is only on the title page

\author{David Karapetyan} % Your name
\institute[PrescriptiveData] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
PrescriptiveData \\ % Your institution for the title page
\medskip
\textit{dkarapetyan@prescriptivedata.io} % Your email address
}
\date{\today} % Date, can be changed to a custom date

\begin{document}

\begin{frame}
\titlepage % Print the title page as the first slide
\end{frame}

\begin{frame}
\frametitle{Overview} % Table of contents slide, comment this block out to remove it
\tableofcontents % Throughout your presentation, if you choose to use \section{} and \subsection{} commands, these will automatically be printed on this slide as an overview of your presentation
\end{frame}

%----------------------------------------------------------------------------------------
%	PRESENTATION SLIDES
%----------------------------------------------------------------------------------------

%------------------------------------------------
\section{Background} % Sections can be created in order to organize your presentation into discrete blocks, all sections and subsections are automatically printed in the table of contents as an overview of the talk
%------------------------------------------------

\subsection{TPO}
\begin{frame}
\frametitle{Background of TPO}
\begin{itemize}
	\item Columbia/TPO was written by a team of 8 Masters and Ph.D students in Statistics
	\item Average salary of the whole team, aggregate, would be $8$ times mine. 
	\item Period of time was 3 years, with additional assistance from developers at Selex
	\item Average energy savings for the buildings, even with prediction accuracies, was stated at $\$500,000$.
	\item Massive amounts of data and code were lost or mismanaged by both. This is evident
		from the SQL dumps that are currently available.
\end{itemize}
\end{frame}

\subsection{Larkin}
\begin{frame}
	\frametitle{Background of Larkin}
	\begin{itemize}
	\item The prediction engine for Larkin was written from scratch solely by David Karapetyan (D.K.)
	\item The benchmark engine was written by Ashish Gagneja, but leverages much of the codebase
		of the prediction engine (the weather underground code pulling weather and munging it, for example)
	\item The prediction engine was written despite extremely limited, reliable data available for testing.
	\item Furthermore, D.K. has filled the roles of database administrator, and project manager for the 
	analytics codebase, until the arrival of Ricardo Cid.
	\item A simple heuristic for computing savings would be that, the accuracy of the models is well over twice that of TPO, and so savings greater than $\$500,000 * 2 = \$1,000,000$. See the next two slides for more information.
\end{itemize}
\end{frame}

\section{Prediction Results and Accuracy}
\subsection{TPO}
%------------------------------------------------
\begin{frame}
\frametitle{TPO Prediction Results and Accuracy}
\begin{itemize}
	\item Models are \underline{$41\%$ accurate} for 345 Park. That is, for every 10 startup time predictions, roughly only 4 are correct by TPO
	\item On average, the \underline{predicted TPO startup times are $13$ minutes off} from the actual startup times.
\item More importantly, the standard deviations of the predicted startup times is 
	\underline{2 hours and 47 minutes off} from the actual startup times. HIGHLY VARIABLE.
\end{itemize}
\end{frame}

\subsection{Larkin}
\begin{frame}
\frametitle{Larkin Prediction Results and Accuracy}
\begin{itemize}
	\item Models are \underline{$98\%$ accurate} for 345 Park. That is, for every 10 startup time predictions, roughly all 10 are correct by Larkin.
	\item On average, the \underline{predicted Larkin startup times are $2$ minutes off} from the actual startup times.
\item More importantly, the standard deviations of the predicted startup times is 
	\underline{3 minutes off} from the actual startup times. HIGHLY RELIABLE.
\end{itemize}
\end{frame}

\section{Conclusion}
\begin{frame}
	\frametitle{Conclusion}
Given D.K.'s many responsibilities and exemplary work at PrescriptiveData, his salary, benefits, and general recognition by management are not aligned with his output, nor what the market currently offers to candidates and employees with similar accomplishments, responsibilities, and ability.
\end{frame}
%------------------------------------------------


\end{document} 
